The population of long-period transiting exoplanets \vspace{-3\baselineskip}

### 2016-07-17 document/ms.tex
typo
comments about multis

@@

Assuming a Poisson likelihood, the occurrence rate density in a volume
$V$~--~defined as $P_\mathrm{min} \le P < P_\mathrm{max}$ and
$R_\mathrm{min} \le R < R_\mathrm{max}$~--~is
\citep[see, for example, the Appendix of][]{Foreman-Mackey:2014}
\begin{eqnarray}\eqlabel{rate-density}
\Gamma_V \equiv \frac{\dd^2 N}{\dd\ln P\dd\ln R} &=&
    \frac{C(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
         {Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
\end{eqnarray}
where $N$ is the expected number of planets per G/K dwarf, $C(\cdots)$ is the
number of detected planets in the volume, and
\begin{eqnarray}
Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max}) &=&
    \sum_{k=1}^{K} \int p(\params_{\{P,\,R\}})\,
    Q_k(\params)\,\bvec{1}[P,\,R\in V]\dd \params
\end{eqnarray}
where $p(\params_{\{P,\,R\}})$ is the prior distribution of all the parameters
except the period and radius and $\bvec{1}[\cdot]$ is 1 if the argument is
satisfied and 0 otherwise.
Using the $J$ injections sampled uniformly in period and radius and other
parameters from $p(w_{\{P,\,R\}})$,
\begin{eqnarray}\eqlabel{approxnorm}
Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max}) &\approx&
    \frac{K}{J}\,\sum_{j=1}^{J} Q_k(w^{(j)})
\end{eqnarray}
where the sum is over all injections in the volume $V$.

>>>>

Of the \numcands\ candidates, \numinner\ have known inner planets with three
or more observable transits \citep{Coughlin:2016}.
Given the fact that only \numkois\ of the \numtargets\ targets have known
planets, this means that of the systems with known inner planets, \fracinner\
have outer transiting planets with one or two transits detectable by our
search.
This fraction is nearly a factor of 20 larger than the same number for targets
with no known inner transiting planets: $\fracnoinner$.
This difference cannot be accounted for by differences in completeness between
targets with known planets and without because the average detection
efficiency for both populations is consistent within sampling uncertainty.
This suggests that these long-period planets are preferentially aligned with
the plane of any inner planets but a more detailed analysis would be needed to
make a quantitative statement \citep[see, for example,][]{Tremaine:2012,
Fang:2012, Ballard:2016, Moriarty:2015}.

@@

Assuming a Poisson likelihood, the occurrence rate density in a volume
$V$~--~defined as $P_\mathrm{min} \le P < P_\mathrm{max}$ and
$R_\mathrm{min} \le R < R_\mathrm{max}$~--~is
\citep[see, for example, the Appendix of][]{Foreman-Mackey:2014}
\begin{eqnarray}\eqlabel{rate-density}
\Gamma_V \equiv \frac{\dd^2 N}{\dd\ln P\dd\ln R} &=&
    \frac{C(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
         {Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max})}
\end{eqnarray}
where $N$ is the expected number of planets per G/K dwarf, $C(\cdots)$ is the
number of detected planets in the volume, and
\begin{eqnarray}
Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max}) &=&
    \sum_{k=1}^{K} \int p(\params_{\{P,\,R\}})\,
    Q_k(\params)\,\bvec{1}[P,\,R\in V]\dd \params
\end{eqnarray}
where $p(\params_{\{P,\,R\}})$ is the prior distribution of all the parameters
except the period and radius and $\bvec{1}[\cdot]$ is 1 if the argument is
satisfied and 0 otherwise.
Using the $J$ injections sampled uniformly in period and radius and other
parameters from $p(w_{\{P,\,R\}})$,
\begin{eqnarray}\eqlabel{approxnorm}
Z(P_\mathrm{min},\,P_\mathrm{max};\,R_\mathrm{min},\,R_\mathrm{max}) &\approx&
    \frac{K\,V}{J}\,\sum_{j=1}^{J} Q_{k_j}(w^{(j)})
\end{eqnarray}
where the sum is over all injections in the volume $V$.
